Plots and tables summarizing results of Poisson simulations

### 2018-12-21 analysis/poisson.Rmd
wflow_publish("poisson.Rmd")

```{r get-spikes-results, echo=FALSE, eval=TRUE}
mise.cb.table  <- cbind(mise.cb.1[methods],
                        mise.cb.8[methods],
                        mise.cb.128[methods])
mise.b.table   <- cbind(mise.b.1[methods],
                        mise.b.8[methods],
                        mise.b.128[methods])
rownames(mise.b.table)   <- table.row.names
rownames(mise.cb.table)  <- table.row.names
colnames(mise.b.table)   <- table.col.names
colnames(mise.cb.table)  <- table.col.names
```

@@

```{r, results="asis"}
print(xtable(mise.cb.table,caption="Comparison of methods for denoising Poisson data for the ``Clipped Blocks'' test function for 3 different (min,max) intensities ((0.01,3), (1/8,8), (1/128,128)). Performance is measured using MISE over 100 independent datasets, with smaller values indicating better performance. Values colored in red indicates the smallest MISE amongst all methods for a given (min, max) intensity.",label="table:pois_cb",digits=2),type = "html")
```

@@

```{r, results="asis"}
print(xtable(mise.b.table,caption="Comparison of methods for denoising Poisson data for the ``Bumps'' test function for 3 different (min,max) intensities ((0.01,3), (1/8,8), (1/128,128)). Performance is measured using MISE over 100 independent datasets, with smaller values indicating better performance. Values colored in red indicates the smallest MISE amongst all methods for a given (min, max) intensity.",label="table:pois_b",digits=2),type = "html")
```

>>>>

@@

This table summarizes the results from the Clipped Blocks simulations:

```{r cb-table, results="asis"}
mise.cb.table <- cbind(mise.cb.1[methods],
                       mise.cb.8[methods],
                       mise.cb.128[methods])
rownames(mise.cb.table) <- table.row.names
colnames(mise.cb.table) <- table.col.names
print(xtable(mise.cb.table,caption = " "),type = "html",
      html.table.attributes = "border=0")
```

```{r cb-violin-plots, fig.height=3.5, fig.width=10}
mise.hf.ti.r.cb.1   <- colMeans(rbind(mise.hf.ti.r.4.cb.1,
                                      mise.hf.ti.r.5.cb.1,
                                      mise.hf.ti.r.6.cb.1,
			  						  mise.hf.ti.r.7.cb.1))
mise.hf.ti.r.cb.8   <- colMeans(rbind(mise.hf.ti.r.4.cb.8,
                                      mise.hf.ti.r.5.cb.8,
                                      mise.hf.ti.r.6.cb.8,
									  mise.hf.ti.r.7.cb.8))
mise.hf.ti.r.cb.128 <- colMeans(rbind(mise.hf.ti.r.4.cb.128,
                                      mise.hf.ti.r.5.cb.128,
                                      mise.hf.ti.r.6.cb.128,
									  mise.hf.ti.r.7.cb.128))
pdat1 <-
  data.frame(method = factor(rep(method.labels,each = m),method.labels),
             mise   = c(mise.hf.ti.r.cb.1,mise.BMSM.cb.1,mise.ash.cb.1))
pdat8 <-
  data.frame(method = factor(rep(method.labels,each = m),method.labels),
             mise   = c(mise.hf.ti.r.cb.8,mise.BMSM.cb.8,mise.ash.cb.8))
pdat128 <-
  data.frame(method=factor(rep(method.labels,each = m),method.labels),
             mise  =c(mise.hf.ti.r.cb.128,mise.BMSM.cb.128,mise.ash.cb.128))
create.violin.plots(pdat1,pdat8,pdat128)
```

@@

This table summarizes the results from the Bumps simulations:

```{r bumps-table, results="asis"}
mise.b.table <- cbind(mise.b.1[methods],
                      mise.b.8[methods],
                      mise.b.128[methods])
rownames(mise.b.table) <- table.row.names
colnames(mise.b.table) <- table.col.names
print(xtable(mise.b.table,caption = " "),type = "html",
      html.table.attributes = "border=0")
```

```{r bumps-violin-plots, fig.height=3.5, fig.width=10}
mise.hf.ti.r.b.1 = colMeans(matrix(c(mise.hf.ti.r.4.b.1, mise.hf.ti.r.5.b.1, mise.hf.ti.r.6.b.1, mise.hf.ti.r.7.b.1), byrow = TRUE, nr = 4))
mise.hf.ti.r.b.8 = colMeans(matrix(c(mise.hf.ti.r.4.b.8, mise.hf.ti.r.5.b.8, mise.hf.ti.r.6.b.8, mise.hf.ti.r.7.b.8), byrow = TRUE, nr = 4))
mise.hf.ti.r.b.128 = colMeans(matrix(c(mise.hf.ti.r.4.b.128, mise.hf.ti.r.5.b.128, mise.hf.ti.r.6.b.128, mise.hf.ti.r.7.b.128), byrow = TRUE, nr = 4))
pdat1 <-
  data.frame(method = factor(rep(method.labels,each = m),method.labels),
             mise   = c(mise.hf.ti.r.cb.1,mise.BMSM.cb.1,mise.ash.cb.1))
pdat8 <-
  data.frame(method = factor(rep(method.labels,each = m),method.labels),
             mise   = c(mise.hf.ti.r.cb.8,mise.BMSM.cb.8,mise.ash.cb.8))
pdat128 <-
  data.frame(method=factor(rep(method.labels,each = m),method.labels),
             mise  =c(mise.hf.ti.r.cb.128,mise.BMSM.cb.128,mise.ash.cb.128))
create.violin.plots(pdat1,pdat8,pdat128)
```
